\documentclass[../weekly]{subfiles}

\begin{document}
\letAswatheertha

\noindent Week 9 mainly focused on finalizing the component procurement list for the rail-based motion system. The objective for this week was to identify all essential electronic parts, verify their availability, and prepare a clean, well-documented list with quantities, unit prices, and purchase URLs. This ensures smooth progress for the upcoming hardware implementation phase.

\subsection{Week 9 Progress Summary}
\begin{enumerate}

    \item \textbf{Component Procurement Planning:}
    \begin{itemize}
        \item A complete component list for the motion system controller and drive circuitry was prepared.
        \item Each item was cross-checked for pricing, availability, and compatibility with the existing design.
        \item Purchase URLs were recorded to simplify ordering and avoid last-minute confusion.
    \end{itemize}

    \item \textbf{Circuit Integration Preparation:}
    \begin{itemize}
        \item Verified that selected components match the electrical requirements of the rail system.
        \item Ensured DRV8825 drivers, limit switches, and the ATmega328P board align with the existing schematic pins.
        \item Capacitor ratings and motor specifications were validated for stable operation.
    \end{itemize}

\end{enumerate}

\subsection{Component List (with URLs)}
\begin{table}[h!]
\centering
\begin{tabular}{lll}
\hline
\textbf{Component} & \textbf{Quantity \& Price(in rupees)} & \textbf{Purchase Link} \\
\hline
ATmega328P Development Board & 1 × 199 & \href{https://robu.in/product/atmega328p-5v-nano-v3-0-development-board-16mhz-ch340-type-c/}{Link} \\
DRV8825 Stepper Driver & 2 × 89 & \href{https://robu.in/product/drv8825-stepper-motor-driver-with-aluminum-heat-sink/}{Link} \\
NEMA17 Stepper Motor & 2 × 755 & \href{https://robu.in/product/nema17-ks42sth34-1504a-stepper-motor-1-5a-34mm/}{Link} \\
100\,µF Capacitors & 2 × 2.11 & \href{https://robu.in/product/100-uf-35v-through-hole-electrolytic-capacitor-dip-pack-of-10/}{Link} \\
Limit Switch (Endstop) & 2 × 7.43 & \href{https://www.etstore.in/products/g7661?_pos=1&_psq=limit+switch&_ss=e&_v=1.0}{Link} \\
\hline
\end{tabular}
\caption{Component list for Week 9 with cost and purchase links}
\end{table}

\bigskip
\noindent\textbf{Total Estimated Cost: 1906.08}

\end{document}
