\documentclass[conference]{IEEEtran}

\input{preamble.tex}

\begin{document}

\title{Seed Incubation Plant}

\author{
    \IEEEauthorblockN{Anjana Roy}
    \IEEEauthorblockA{\emph{Dept. of Electronics \& Communication}\\ \emph{Rajiv Gandhi Institute of Technology}\\ Kerala, India\\ 22bl14920@rit.ac.in}
    \and
    \IEEEauthorblockN{Aswatheertha T T}
    \IEEEauthorblockA{\emph{Dept. of Electronics \& Communication}\\ \emph{Rajiv Gandhi Institute of Technology}\\ Kerala, India\\ 22bl14661@rit.ac.in}
    \linebreakand
    % \and
    \IEEEauthorblockN{Athira Madhusoodanan}
    \IEEEauthorblockA{\emph{Dept. of Electronics \& Communication}\\ \emph{Rajiv Gandhi Institute of Technology}\\ Kerala, India\\ 22bl14998@rit.ac.in}
    \and
    \IEEEauthorblockN{Daniel V Mathew}
    \IEEEauthorblockA{\emph{Dept. of Electronics \& Communication}\\ \emph{Rajiv Gandhi Institute of Technology}\\ Kerala, India\\ 22bl14682@rit.ac.in}
}

\maketitle

\begin{abstract}
    \noindent The \textbf{Seed Incubation Plant} with \textbf{EMCU} and \textbf{GMU}
    aims to optimize the \emph{germination} and \emph{growth
    process} of \emph{seeds} by providing a \emph{controlled} and
    \emph{monitored environment}.
    %%
    Manual methods are prone to \emph{human error}, requiring constant
    attention to environmental factors which can \emph{fluctuate} and
    \emph{adversely affect seed growth} and may lead to \emph{suboptimal
    results}.
    %%
    In most cases \emph{migrating} to an automated system is not
    \emph{economically feasible}, as it may require importing various
    equipments.Thus, an \emph{indigenous} implementation using a widely
    available \emph{controller} is an alternative solution.
    %%
    This system aims to realize the \emph{environment monitoring and control
    system} which will \emph{monitor} and \emph{control} various aspects that
    influence the optimal growth of the seedling, including \textbf{humidity},
    \textbf{temperature}, \textbf{lighting} and \textbf{soil moisture} by using ESP32
    \emph{microcontroller}. Wifi capabilities of ESP32 ensures
    the accumulation of collected data and presenting it to the user, visually.
    %%
    Along with this, we aims to develop a \emph{growth monitoring unit} powered by a
    fully functional \textbf{TinyML} model that can utilize the limited resources of
    the ESP32 CAM module, enabling close monitoring of different stages of
    seed's germination. In addition, we aim to develop SINC - a fully functional
    companion app to the Seed Incubator.
    %%
    This solution not only tries to improve the \emph{efficiency} and the
    \emph{success rate of seed germination} but also tries to reduce the
    \emph{labour costs} and \emph{energy consumption}, hoping to offer a
    sustainable and reliable alternative to traditional incubation methods.
\end{abstract}

\section{Introduction}

\end{document}
