\def\pOneProgress{0}
\def\pTwoProgress{0}
\def\pThreeProgress{0}
\def\pFourProgress{0}

\newcommand\pOneCmpData{
    {Complete the list of components.}/0,
    {Collect the url of the components.}/0,
    {Search and refer the linear carriage designs.}/0,
    {Start the linear carriage design.}/0
}

\newcommand\pTwoCmpData{
    {Final Component list .}/0,
    {Finding suitable sites for purchase.}/0,
    {Component list preparation.}/0,
    {Url collection for ordering.}/0,
    {Ordering of components.}/0,
    {Atmega programming research.}/0,
    {Specifications study of components.}/0
}

\newcommand\pThreeCmpData{
    {Figure out how to redo the live feed screen UI.}/0,
    {Correct the code for live feed from esp cam.}/0,
    {Plan the UI for showing connection status.}/0,
    {Redo the existing UI.}/0,
    {Improvise according to the updated requirements.}/0,
    {Figure out the code for connecting to both esp32.}/0
}

\newcommand\pFourCmpData{
    {CAD Design of Implementable Core Block.}/0,
    {CAD Design of Exhaust Branches.}/0,
    {Core Block Mount Base Plate.}/0,
    {Core Block Mount Top Cover.}/0,
    {Reservoir Connectors.}/0,
    {Drill Holes for Reservoir.}/0,
    {Drill Holes for Electronics Bay.}/0,
    {Drill Holes for Top Hatch.}/0,
    {Drill Holes for Core Block Mount.}/0,
    {Start Working on Painting the Frame.}/0,
    {Figure out how to attach mid layer (PVC Foam and polycarbonate) to plywood.}/0,
    {Rough design of mid layer and air moisture cycler interface.}/0,
    {Rough design of mid layer and exhaust branch interface.}/0,
    {Figure out how to attach GMU rail to plywood, with mid layer in-between.}/0,
    {CAD design of core block chambers.}/0,
    {CAD design of core block panels.}/0,
    {CAD design of core block and exhaust branches interface.}/0,
    {CAD design of exhaust branches.}/0,
    {CAD design of mid layer (with PVC foam) for incubator area.}/0,
    {CAD design of mid layer (with polycarbonate) for incubator area base.}/0,
    {Mark and cut foam pieces for incubator area mid layer.}/0,
    {Start assembling foam mid layer.}/0
}

